doe-pkgs-analysis

### 2021-10-03 analysis/doe-pkgs-analysis.Rmd
Add year in sankey plot.

# pivot longer the data frame by its type 
pkg_tidy_long_type <- pkg_tidy %>%
  unnest(type) %>%
  unnest(date) %>%
  unnest(domain) %>%
  mutate(year = year(ymd(date))) 
```

```{r}
# summarise the packages based on its type
pkg_tidy_long_type %>%
  filter(relevance != "no") %>%
  group_by(type) %>%
  count() %>%
  arrange(desc(n))
```

@@

```{r}
sankey_data <- pkg_tidy_long_type %>%
  select(year, domain, type) %>%
  group_by(domain, type) %>%
  count() %>%
  ungroup()

@@

>>>>

# pivot longer the data frame by its type 
pkg_tidy_long_type <- pkg_tidy %>%
  unnest(type) %>%
  unnest(date) %>%
  unnest(domain) %>%
  mutate(year = year(ymd(date)))

```{r}
# summarise the packages based on its type
pkg_type <- pkg_tidy_long_type %>%
  group_by(L2) %>%
  slice_head(n = 1) %>%
  mutate(year = factor(year, level = c("2009", "2011", "2012", "2013",
                                       "2014", "2015", "2016", "2017",
                                       "2018", "2019", "2020", "2021")))
```

@@

```{r}
sankey_data <- pkg_type %>%
  select(domain, type) %>%
  group_by(domain, type) %>%
  count() %>%
  ungroup()

@@

```{r}
sankey_data <- pkg_type %>%
  select(domain, year) %>%
  group_by(domain, year) %>%
  count() %>%
  ungroup()

year <- sankey_data %>%
  distinct(node = year)

db_sankey <- rbind(domain, year)
